---
title: "R Notebook"
output: html_notebook
---

DBI asbtract the data from realtion databases management system which put customise in frontend of r..and make assumption.

```{r}
library(DBI)
```
Atfirst we have to build connection by using this function of DBI

Here RSQLite is used as package in R which has there own database file[SQLite()].  Which DBI used to extract data.

```{r}
dbConnect(RSQLite::SQLite(), dpname = ":memory:")
```
Here SQLite is driver of package RQSLite database file and could not show result  because there is no database file named called "pritha"

```{r}
mom<-dbConnect(RSQLite::SQLite(),dbname=":pritha:")
```
memory is saved as file 
```{r}
mom <- dbConnect(RSQLite::SQLite(), ":memory:")
```

```{r}
mom
```
```{r}
dbListTables(mom)
```
character(0) says there is no table of data as its "memory" only.  
so to create the table of mtcars list or any table of data into the driver(SQLite)
DBI used in r is very useful because it allow  to input data of dataframes into database.

```{r}
dbWriteTable(mom, "mtcars",mtcars)
```

```{r}
dbListTables(mom)
```
so it show as table 1

```{r}
dbListFields(mom, "mtcars")
```
```{r}
dbReadTable(mom,"mtcars")
```

```{r}
table=dbReadTable(mom,"mtcars")
```

Now upper example we have created data and extract in in R through DBI but actually in real world we have to face SQL and extract the data from  there SQL database into R with SQL code

like this code
```{r}
dbSendQuery(mom, "SELECT* FROM mtcars WHERE cyl=4")
```
```{r}
res=dbSendQuery(mom, "SELECT* FROM mtcars WHERE cyl=4")
dbFetch(res)
```

```{r}
res
```


```{r}
dbClearResult(res)
```
we have to close it



