---
title: " select verb"
output: html_notebook
---


dplyr is a grammar of data manipulation, providing a consistent set of verbs that help you solve the most common data manipulation challenges:

mutate() = adds new variables that are functions of existing variables
select() = picks variables based on their names.
filter() = picks cases based on their values.
summarise() = reduces multiple values down to a single summary.
arrange() = changes the ordering of the rows.

These all combine naturally with group_by() which allows you to perform any operation “by group”. You can learn more about them in vignette("dplyr"). As well as these single-table verbs, dplyr also provides a variety of two-table verbs, which you can learn about in vignette("two-table").

If you are new to dplyr, the best place to start is the data transformation chapter in R for data science




```{r}
which(letters=="b")
```
SELECT VERB  MEANS SELECTING COLOUMNS 
WE CAN CHANGE OR MANIPULATE THE COLOUMNS OF EXISTING DATAFRAME BUT CANNOT ADD NEW VARIABLE TO THE EXISTING DATAFRAME (WHICH IS DEFAULT i,e mtcars)

```{r}
starwars
```
IF WE WANT ONLY COLUMNS between  eye_color to species 

```{r}
colnames(starwars)
```
```{r}
which(colnames(starwars)=="eye_color")
```
```{r}
which(colnames(starwars)=="species")
```
```{r}
starwars %>% select(6:11)
```
same result by putting names of the function which makes convinent
```{r}
starwars %>% select(which(colnames(starwars)=="eye_color"):which(colnames(starwars)=="species"))
```
OR puting dot in starwars after select funtion which pipe denote to dataframe starwars.
```{r}
starwars %>% select(which(colnames(.)=="eye_color"):which(colnames(.)=="species"))
```
also we can change the data as convinent
```{r}
starwars %>% select(11,10,9,8,7,6)
```

or we can direct put the name of the column as r is smart
SAME RESULT

```{r}
starwars %>% select(species:eye_color)
```
AND ALSO REMOVE THE COLUMN BY PUTTING -SIGN 

```{r}
starwars %>% select(species:eye_color,-sex)
```
everything() is the function within select verb . it is used only in select()
```{r}

```


```{r}
install.packages("waldo")
```


WALDO is the package and compare() is the function that works under waldo.

```{r}
library(waldo)
```

```{r}
t= starwars %>% select(everything())
```

```{r}
compare(t,head(starwars))
```
if i want to see the specific column like from skin_color to species than this can be done and after that all colnames.

```{r}
t %>% select(skin_color:species,everything())
```
now if i want to see the data which contains suffix _color than we write
```{r}
starwars %>% select(hair_color,skin_color,eye_color)
```
Or easier way to do is puting function of dplyr i.e starts_with ,ends_with i.e
```{r}
starwars %>% select(ends_with("color"))
```

```{r}
iris %>% select(starts_with("sepal"))
```
where()
is the function help to find the things like 
```{r}
 starwars %>% select(where(is.integer))
```
```{r}
starwars %>% select(where(is.character))
```
   ! = this denote not....(means no color at the end)
   
```{r}
starwars %>% select(!ends_with("color"))
```

```{r}
 starwars %>% select(starts_with("mass"), ends_with("color"))
```




